%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.1 (9/2/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\usepackage{fontawesome}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Ferron}{Hanse}{Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
15 Corner Lewis \& Third Avenue
Barataria, San Juan
Trinidad
~
\faPhone{ (868) 764 4172}
~
\href{mailto:ferronrsmith@gmail.com}{\faInbox{ ferronrsmith}}
\href{http://ferronrsmith.github.io}{\faGithub{ ferronrsmith}}
\href{http://linkedin.com/in/ferronrsmith}{\faLinkedin{ ferron.hanse}}
\section{languages}
english (mother tongue)
\section{programming}
{\color{red} $\varheartsuit$} JavaScript
Python, C\#, PHP
Java, Spring 
CSS3 \& HTML5
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2013--2015}
{Masters {\normalfont in Computer Science}}
{The University of West Indies, St. Augustine}
{\emph{Using Computer Vision Action Classification Techniques to Detect Drivers with Cellphones} \\ This thesis explored the idea of using computer vision to detect the use of cellphones. Which can then be used by Law Enforcment authority to detect and prosecute delinquent road users }
%------------------------------------------------
\entry
{2007--2008}
{Bachelor {\normalfont  in Computer Science}}
{The University of West Indies, Mona}
{}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

%------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2014--Now}
{\textsc{Groupby Inc}}
{San Juan, Trinidad}
{\emph{Software Engineer} \\
\begin{itemize}
\item Participate in the process of software development including design, implementation, and maintenance in ASP.NET, Java or Python based software projects
\item Provide input to the functional specifications and the project requirements
\item Participate in development meetings, and assume full responsibility for your portion of the development effort
\item Write code using one of the aforementioned client side and server side technologies
\item Develop project documentation, including operational procedures, functional specifications, technical specifications
\item Complete peer code reviews and propose improvements and enhancements
\item Contribute to our knowledge base by developing best practice implementation documentation
\end{itemize}}
\end{entrylist}

%------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2014--2014}
{\textsc{Medullan Trinidad Limited}}
{D'Adbadie, Trinidad}
{\emph{Senior Software Developer} \\
Medullan Senior Software Developers responsibilities: \\
\begin{itemize}
\item Responsible for planning, processing and performing all jobs in an efficient manner with no assistance from the supervisor
\item Working closely with upper management.
\item Design and develop programming systems making specific determinations about system performance.
\item Analyze, design, coordinate and supervise the development of software systems to form a basis for the solution of information processing problems.
\item Responsible for developing new programs and proofing the program to develop needed changes to assure production of a quality product.
\item Responsible for development of new programs, analyzes current programs and processes, and making recommendations which yield a more cost effective product.
\item Writes, edits, and debugs new computer programs for assigned projects, including necessary records and desired output.
\item Tests new programs to ensure that logic and syntax are correct, and that program results are accurate; assists lower-level programmers with programming assignments.
\item Document code consistently throughout the development process by listing a description of the program, special instructions, and any changes made in database tables on procedural, modular and database level.
\item Responsible for reading, understanding, and utilizing all part and assembly prints, forms, spreadsheets, bills of material, specification sheets, and technical references.
\item Responsible for utilizing tools and equipment involved in performance of essential functions of programming including measuring instruments.
\item Search, summarize and keep the team abreast of strategic information from all sources
\item Provide feedback to analysis/training staff about performance considerations / usability issues concerning software specifications and implementation.
\item Research and recommend software tools to management.
\item Provide assistance to testers and support personnel as needed to determine system problems.
\end{itemize}}
\end{entrylist}

%------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2010-2014}
{\textsc{Medullan Trinidad Limited}}
{D'Adbadie, Trinidad}
{\emph{Software Developer} \\
Responsible for delivering a component of custom software through the full software development
lifecycle, including interaction design, solution definition, implementation, and support.
Worked in a collaborative environment to develop enterprise-level applications
using object oriented and service oriented technologies. Regular interactions with clients to understand
their business, their business needs and how best to implement technology to meet
those needs as I contribute to the full lifecycle of projects from solution definition through
to implementation. Responsible for producing quality custom software as well as collaborating
with a team of 1-4 software developers, producing plans to accomplish project work and partnering on
the execution of those plans to achieve the project end goals.}
%------------------------------------------------
\end{entrylist}

%------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2007-2010}
{\textsc{University of the West Indies}}
{Mona, Jamaica}
{\emph{Lab Technician} \\
Worked as a Lab Technician at UWI helping Computer Science student with assignments, 
projects, maintain the computers in the lab.}
%------------------------------------------------
\end{entrylist}

%------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2008-2009}
{\textsc{First Global Bank}}
{New Kingston, Jamaica}
{\emph{Computer Programmer} \\
Responsible for designing custom reports for the accounting staff using Crystal Reports and ASP.NET}
%------------------------------------------------
\end{entrylist}

%------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2006-2007}
{\textsc{Baritta Investment}}
{New Kingston, Jamaica}
{\emph{Intern} \\
Rated "truly distinctive" for Analytical Skills and Teamwork.}
%------------------------------------------------
\end{entrylist}

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2005}
{Jamaica College}
{}
{Most Outstanding Computer Science Student.}

%------------------------------------------------
\entry
{1998-2000}
{Jamaica College}
{}
{Top Computer Science Student.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, web design, web app creation, software design \\ 
\textbf{personal:} backgammon, cooking, running


%----------------------------------------------------------------------------------------

\end{document}